Unigram entropy in childes

### 2018-08-20 Unigram Positional Entropy.Rmd
Updated non-English to include stemming

get_noneng_entropies <- function(role, sen_length, utterances) {

  if(role == "Target_Child") {
    sub_utterances <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1) 
  } else {
     sub_utterances <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1)
  }

@@

  tokens <- sub_utterances %>%
    filter(length == sen_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n())

@@

entropies <- map(2:10, ~get_noneng_entropies("not child", .x, okayama_utterances)) %>%
  bind_rows() %>% filter(word_order <= length)

@@

entropies_child <- map(2:10, ~ get_noneng_entropies("Target_Child", .x, okayama_utterances)) %>%
  bind_rows() %>% filter(word_order <= length)

@@

ggplot(entropies_all, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper, color = role)) +
  facet_wrap(~ length) + 
  geom_pointrange(position = position_dodge(.25)) +
  geom_smooth(se = F) +
  ggtitle("Child and Adult Positional Entropy vs. Word Position (Japanese Okayama corpus)")
```

>>>>

get_noneng_entropies <- function(role, sen_length, utterances, langue) {

  if(role == "Target_Child") {
    sub_utterances <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(stems = wordStem(gloss, language = langue)) %>% 
      mutate(length = str_count(stems, " ") + 1) 
  } else {
     sub_utterances <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(stems = wordStem(gloss, language = langue)) %>% 
      mutate(length = str_count(stems, " ") + 1)
  }

@@

  tokens <- sub_utterances %>%
    filter(length == sen_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stems) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n())

@@

entropies <- map(2:10, ~get_noneng_entropies("not child", .x, wagner_utterances, "german")) %>%
  bind_rows() %>% filter(word_order <= length) #some utterances have ""

@@

entropies_child <- map(2:10, ~ get_noneng_entropies("Target_Child", .x, wagner_utterances, "german")) %>%
  bind_rows() %>% filter(word_order <= length)

@@

ggplot(entropies_all, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper, color = role)) +
  facet_wrap(~ length) + 
  geom_pointrange(position = position_dodge(.25)) +
  geom_smooth(se = F) +
  ggtitle("Child and Adult Positional Entropy vs. Word Position (German Wagner corpus with stemming)")
```
